Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-01-21 manuscript/manuscript.Rmd
updated figure 1

Figures
-------
```{r figure_1, dependson="plot-options", fig.cap="Boxplots of model residuals for one-step-ahead forecasts at each observation year for each quadrat. Residuals represent the difference in observed and predicted cover change from year $t-1$ to year $t$. Each one-step forecast was simulated 100 times for each quadrat. Note that the y-axes vary across panels.", fig.width=8, fig.height=8, cache=FALSE, results='hide'}
resD <- readRDS("../montana/quadBM/simulations/quadBM_oneStep_ResidualsFullModel.rds")
resDny <- readRDS("../montana/quadBM/simulations/quadBM_oneStep_ResidualsNoYear.rds")
resD$simtype <- rep("full", nrow(resD))
resDny$simtype <- rep("noyear", nrow(resDny))
resDall <- rbind(resD, resDny)
# nSims <- length(unique(resD$sim))
diffD <- ddply(resDall, c("year", "species", "simtype"), summarise,
               avgDiff = mean(resids, na.rm = TRUE),
#                upDiff75 = quantile(resids, probs = 0.8775, names=FALSE, na.rm = TRUE),
#                dnDiff75 = quantile(resids, probs = 0.1225, names=FALSE, na.rm = TRUE),
               dnDiff95 = quantile(resids, probs = 0.025, names=FALSE, na.rm = TRUE),
               upDiff95 = quantile(resids, probs = 0.975, names=FALSE, na.rm = TRUE))
# ggplot(diffD, aes(color=simtype))+
#   geom_hline(aes(yintercept=0), linetype=2, color="grey50")+
#   geom_point(aes(x=year, y=avgDiff), size=3, position=position_dodge(width=0.5))+
#   geom_errorbar(aes(x=year, ymax=upDiff95, ymin=dnDiff95), width=0.00001, position=position_dodge(width=0.5))+
# #   geom_errorbar(aes(x=year, ymax=upDiff75, ymin=dnDiff75), size=1, width=0.00001, position=position_dodge(width=0.5))+
#   facet_grid(species~., scales = "free_y")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
# 
# ggplot(resDall)+
#   geom_hline(aes(yintercept=0), linetype=2)+
# #   geom_line(data=diffD, aes(x=year, y=avgDiff, group=species), color="purple", alpha=0.5)+
# #   stat_smooth(data=diffD, aes(x=year, y=avgDiff, group=species), color="lightblue", se = FALSE, size=1)+
#   geom_boxplot(aes(x=year, y=resids, fill=simtype), outlier.shape = 1, width=0.3, outlier.size = 0.5)+
#   facet_grid(species~., scales = "free_y")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
myCols <- c("#237DA4", "#7ECAD0")
p1 <- ggplot(subset(resDall, species=="BOGR"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=year, y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
#   coord_cartesian(ylim = c(-50, 45))+
  ggtitle(expression(italic("B. gracilis")))+
  guides(fill=FALSE)
p2 <- ggplot(subset(resDall, species=="HECO"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=year, y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols, labels=c("Year effects", "No year effects"))+
  ggtitle(expression(italic("H. comita")))+
  coord_cartesian(ylim = c(-10, 5))+
  guides(fill=guide_legend(title=""))+
  theme(legend.position=c(0.7,0.2))
p3 <- ggplot(subset(resDall, species=="PASM"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=year, y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  ggtitle(expression(italic("P. smithii")))+
  guides(fill=FALSE)+
  coord_cartesian(ylim = c(-2.5, 2.5))
p4 <- ggplot(subset(resDall, species=="POSE"))+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_boxplot(aes(x=year, y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values=myCols)+
  ggtitle(expression(italic("Poa secunda")))+
  guides(fill=FALSE)+
  coord_cartesian(ylim = c(-50, 10))
pFinal <- grid.arrange(p1,p2,p3,p4, ncol=2, nrow=2)
# pFinal

>>>>

Figures
-------
```{r figure_1, dependson="plot-options", fig.cap="Boxplots of model residuals for one-step-ahead forecasts at each observation year for each quadrat. Residuals represent the difference in observed and predicted cover change from year $t-1$ to year $t$. Each one-step forecast was simulated 100 times for each quadrat. Note that the y-axes vary across panels.", fig.width=8, fig.height=8, cache=FALSE, results='hide'}
resD <- readRDS("../montana/quadBM/simulations/oneStepResids_YearEffects.rds")
resDny <- readRDS("../montana/quadBM/simulations/oneStepResids_NoYearEffects.rds")
resD$simtype <- rep("full", nrow(resD))
resDny$simtype <- rep("noyear", nrow(resDny))
resDall <- rbind(resD, resDny)

myCols <- c("#237DA4", "#7ECAD0")
# ggplot(resDall, aes(x=resids, fill=simtype))+
#   geom_histogram(alpha=0.5)+
#   facet_grid(.~species, scales = "free_x")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   scale_fill_manual(values=myCols)

# nSims <- length(unique(resD$sim))
diffD <- ddply(resDall, c("year", "species", "simtype"), summarise,
               avgDiff = median(resids, na.rm = TRUE),
               upDiff75 = quantile(resids, probs = 0.8775, names=FALSE, na.rm = TRUE),
               dnDiff75 = quantile(resids, probs = 0.1225, names=FALSE, na.rm = TRUE),
               dnDiff95 = quantile(resids, probs = 0.025, names=FALSE, na.rm = TRUE),
               upDiff95 = quantile(resids, probs = 0.975, names=FALSE, na.rm = TRUE))

ggplot(diffD, aes(color=simtype))+
  geom_hline(aes(yintercept=0), linetype=2, color="grey50")+
  geom_point(aes(x=as.character(year), y=avgDiff), size=3, position=position_dodge(width=0.5))+
  geom_errorbar(aes(x=as.character(year), ymax=upDiff95, ymin=dnDiff95), width=0.00001, position=position_dodge(width=0.5))+
  geom_errorbar(aes(x=as.character(year), ymax=upDiff75, ymin=dnDiff75), size=1, width=0.00001, position=position_dodge(width=0.5))+
  facet_grid(species~., scales = "free_y")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  scale_color_manual(values=myCols)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
# 
# ggplot(resDall)+
#   geom_hline(aes(yintercept=0), linetype=2)+
# #   geom_line(data=diffD, aes(x=year, y=avgDiff, group=species), color="purple", alpha=0.5)+
# #   stat_smooth(data=diffD, aes(x=year, y=avgDiff, group=species), color="lightblue", se = FALSE, size=1)+
#   geom_boxplot(aes(x=year, y=resids, fill=simtype), outlier.shape = 1, width=0.3, outlier.size = 0.5)+
#   facet_grid(species~., scales = "free_y")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
# myCols <- c("#237DA4", "#7ECAD0")
# p1 <- ggplot(subset(resDall, species=="BOGR"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   coord_cartesian(ylim = c(-10, 10))+
#   ggtitle(expression(italic("B. gracilis")))+
#   guides(fill=FALSE)
# p2 <- ggplot(subset(resDall, species=="HECO"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols, labels=c("Year effects", "No year effects"))+
#   ggtitle(expression(italic("H. comita")))+
#   coord_cartesian(ylim = c(-0.5, 0.5))+
#   guides(fill=guide_legend(title=""))+
#   theme(legend.position=c(0.7,0.2))
# p3 <- ggplot(subset(resDall, species=="PASM"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   ggtitle(expression(italic("P. smithii")))+
#   guides(fill=FALSE)+
#   coord_cartesian(ylim = c(-2.5, 2.5))
# p4 <- ggplot(subset(resDall, species=="POSE"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   ggtitle(expression(italic("Poa secunda")))+
#   guides(fill=FALSE)+
#   coord_cartesian(ylim = c(-50, 10))
# pFinal <- grid.arrange(p1,p2,p3,p4, ncol=2, nrow=2)
# pFinal
